### 2013-11-01 regressionModelling.Rmd
restructuring the whole lot. Creative destruction

summary(bisoc.1 <- lmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.2 <- lmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.3 <- lmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.4 <- lmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.5 <- lmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.6 <- lmer(pov.log.social ~ crise+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.7 <- lmer(pov.log.social ~ group1+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.8 <- lmer(pov.log.social ~ uw.gini+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.9 <- lmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.10 <- lmer(pov.log.social ~ wbgi.vae+(1|cntry),
                         family = binomial, data=df))

summary(biind.1 <- lmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial, data=df))
summary(biind.2 <- lmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial, data=df))
summary(biind.3 <- lmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial, data=df))
summary(biind.4 <- lmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial, data=df))
summary(biind.5 <- lmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial, data=df))
summary(biind.6 <- lmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial, data=df))
summary(biind.7 <- lmer(pov.log.individual ~ group1+(1|cntry),
                        family = binomial, data=df))
summary(biind.8 <- lmer(pov.log.individual ~ uw.gini+(1|cntry),
                        family = binomial, data=df))
summary(biind.9 <- lmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial, data=df))
summary(biind.10 <- lmer(pov.log.individual ~ wbgi.vae+(1|cntry),
                         family = binomial, data=df))

summary(soc.0 <- lmer(pov.log.social ~ (1|cntry),
                      family = binomial, data=df))
summary(soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial, data=df))
summary(soc.2 <- lmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+(1|cntry),family = binomial, data=df))
summary(soc.3 <- lmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+gdpchange07.10+(1|cntry),family = binomial, data=df))
summary(soc.4 <- lmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+gdpchange07.10+wbgi.vae+(1|cntry),family = binomial, data=df))

summary(ind.0 <- lmer(pov.log.individual ~ (1|cntry),
                      family = binomial, data=df))
summary(ind.1 <- lmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial, data=df))
summary(ind.2 <- lmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+(1|cntry),family = binomial, data=df))
summary(ind.3 <- lmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+gdpchange07.10+(1|cntry),family = binomial, data=df))
summary(ind.4 <- lmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+gdpchange07.10+wbgi.vae+(1|cntry),family = binomial, data=df))
```

>>>>

summary(bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.7 <- glmer(pov.log.social ~ group1+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.8 <- glmer(pov.log.social ~ uw.gini+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.9 <- glmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data=df))
summary(bisoc.10 <- glmer(pov.log.social ~ wbgi.vae+(1|cntry),
                         family = binomial(logit), data=df))

summary(biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.7 <- glmer(pov.log.individual ~ group1+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.8 <- glmer(pov.log.individual ~ uw.gini+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.10 <- glmer(pov.log.individual ~ wbgi.vae+(1|cntry),
                         family = binomial(logit), data=df))

summary(soc.0 <- glmer(pov.log.social ~ (1|cntry),
                      family = binomial(logit)(logit),
                       data=df.multi))
summary(soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                         past.diff+future.diff+crise+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(soc.2 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(soc.3 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))

summary(ind.0 <- glmer(pov.log.individual ~ (1|cntry),
                      family = binomial(logit),
                       data=df.multi))
summary(ind.1 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                       data=df.multi))
summary(ind.2 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(ind.3 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
```
